Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-03-25 Paper/Paper.tex
slight improvement
application intro redone

\section{Applications}\label{sec:exps2}
In this section we describe two other applications of the clustering
described in this paper: song segmentation, and artist
recognition.  This demonstrates the utility of unsupervised clustering
to supervised tasks. The representation created from large collections
captures meaningful information without being forced to do so.
% Although our algorithm was not devised for any of these
% tasks, but some information contained in the centroids can be
% naturally used.

@@

The clustering method proposed in this work is not
intended to perform well at artist recognition. An obvious fact is that
we lose all timbral information which would be useful. However, we can
imagine that some artist use more often some patterns than others.
Our accuracy result is $23.4\%$ while random
is around $5\%$. 
The confusion matrix can be seen in Figure \ref{fig:conf_mat}.
Details of the experiment follow.

>>>>

\section{Applications}\label{sec:exps2}
In this section we apply the result of our method to two task
not related to clustering. We try to demonstrate that the codewords
we learned capture musically meaningful patterns, at least to
contemporary pop music. This also demonstrates the utility of unsupervised 
clustering to other MIR tasks usually tackled in a supervised
framework. In the first experiment, we show that bar information is retained 
in the codewords. Thus we can discover the bar boundaries for new songs.
The second experiment shows we can discriminate artists
based on the encoding of their songs, hence we can associate artists
with specific codes.

% Although our algorithm was not devised for any of these
% tasks, but some information contained in the centroids can be
% naturally used.

@@

The clustering method proposed in this work is not
intended to perform well at artist recognition. 
In particular,
we lose all timbral information which would be useful. 
However, we can
imagine that some artist use more often some patterns than others.
Our accuracy result is $23.4\%$ while random
is around $5\%$. 
The confusion matrix can be seen in Figure \ref{fig:conf_mat}.
Details of the experiment follow.
